%-------------------------
% Resume 
% Author : Sagnik
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small #1\vspace{-2pt}}

\newcommand{\classesList}[4]{
	\item\small{
		{#1 #2 #3 #4 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textbf{\small #2} \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & \textbf{\small #2}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Subheading list (like Experience sections)
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}


% Bullet item list (like points under each role or project)
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeItemListEnd}{\end{itemize}}



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	%----------HEADING----------
	\begin{center}
		{\Huge \scshape Sagnik Das} \\ \vspace{1em} 
		\small \raisebox{-0.1\height}\faPhone\ 9233110188 ~ \href{mailto:sagnikdas5432@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sagnikdas5432@gmail.com}} ~ 
		\href{https://www.linkedin.com/in/sagnik-das-b550ab224/}{\raisebox{-0.2\height}\faLinkedin\ \underline{sagnik-das-b550ab224}}  ~
		\href{https://github.com/sagnik3788}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/sagnik3788}}
		\vspace{-8pt}
	\end{center}
	
	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Indian Institute of Information Technology and Management, Gwalior}{July 2022 -- July 2027}
	{Integrated M.Tech in Information Technology}{}
	\resumeSubHeadingListEnd
	
	%------RELEVANT COURSEWORK-------
	\section{Relevant Coursework}
	\begin{multicols}{4}
		\begin{itemize}[itemsep=-5pt, parsep=3pt]
			\item Data Structures
			\item Cloud Computing 
			\item Algorithms Analysis
			\item Database Management
			\item Artificial Intelligence
			\item Operating System
			\item OOPS
			\item Computer Architecture
		\end{itemize}
	\end{multicols}
	\vspace*{2.0\multicolsep}
	
	%-----------EXPERIENCE-----------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{\href{https://mentorship.lfx.linuxfoundation.org/project/ca6413f6-6f97-4e41-aad8-8d2bbe17251d}{LFX Mentee at PipeCD (CNCF)}}{June 2025 – Aug 2025}
	{Internship}{Tokyo/Remote}
	\resumeItemListStart
	\resumeItem{Contributed to CNCF’s \textbf{PipeCD}, helping automate and manage \textbf{2,000+} production deployments for companies like	CyberAgent, saving \textbf{500+} engineer-hours/month.}
	\resumeItem{Built a standalone  \textbf{OpenTofu gRPC plugin} fully developed in  \textbf{Go} using GitOps practices, plus a 3-level config system to deploy   \textbf{100+} microservices across multi-cloud, cutting manual IaC effort by \textbf{50\%}.}
	\resumeItem{Implemented SDK-driven automation,  \textbf{plan previews},  \textbf{drift detection}, and  \textbf{auto-rollback}, cutting infra misconfigs by  \textbf{30\%} and cloud costs by  \textbf{20–30\%}.}
	\resumeItemListEnd
	
	
	
	\resumeSubHeadingListEnd
	
	
	
	\vspace{-16pt}
	
	
	%-----------PROJECTS-----------
	\section{Projects}
	\resumeSubHeadingListStart
	
	\resumeProjectHeading
	{\textbf{\href{}{dappergo}} $|$ \emph{Go, gRPC, protobuf}}{Jan 2024 -- Feb 2024}
	\resumeItemListStart
   \resumeItem{Built a lightweight distributed tracing library \textbf{inspired by Google's Dapper} in Go for observing and debugging microservices.}
   \resumeItem{Implemented a \textbf{gRPC-based span collection} system with buffered channel architecture, processing \textbf{10,000+} spans per second without blocking main threads.}
   \resumeItem{Designed context-based trace propagation flowing across \textbf{15+} service boundaries with \textbf{zero} context loss and \textbf{100\%} accurate dependency mapping.}
   \resumeItem{Developed probabilistic sampling reducing overhead by \textbf{80\%} while capturing statistically representative traces with \textbf{<5ms} latency.}
	\resumeItemListEnd
	
	\resumeProjectHeading
	{\textbf{\href{https://github.com/sagnik3788/FlowCD}{FlowCD}} $|$ \emph{Go, Kubernetes API, Git}}{March 2025 -- April 2025}
	\resumeItemListStart
	\resumeItem{Built a lightweight \textbf{GitOps controller} inspired by \textbf{ArgoCD} to automate deployment of \textbf{50+} applications across Kubernetes clusters.}
	\resumeItem{Implemented periodic sync logic to monitor a \textbf{Git repository} for changes and auto-apply updated \textbf{Kubernetes manifests}, ensuring state drift is minimized by \textbf{100\%} within the cluster.}
	\resumeItem{Deployed and tested the controller on a local \textbf{K3s} cluster, achieving \textbf{90\%} faster rollout compared to manual kubectl workflows.}
	\resumeItem{Leveraged \textbf{Go}, native \textbf{Kubernetes API} calls, and Git webhooks for declarative and efficient infrastructure management.}
	\resumeItemListEnd
	
	
	% Remove or adjust any additional \vspace commands here if needed
	
	\resumeSubHeadingListEnd 
	
	%-----------TECHNICAL SKILLS-----------
	% \section{Technical Skills}
	% \begin{itemize}[leftmargin=0.15in, label={}]
		%   \item \small{ \textbf{ML/AI:} PyTorch, Flower, Federated Learning, Transfer Learning }
		%   \item \small{ \textbf{DevOps/Systems:} Docker, Terraform, Argo CD, Kubernetes, Prometheus, Grafana, GitHub Actions, FastAPI }
		%   \item \small{ \textbf{Languages:} Python, Golang }
		% \end{itemize}
	% \vspace{-16pt}
	
	
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt ]
		\item \small{ \textbf{ML/AI:} PyTorch , Flower, Federated Learning , Transfer Learning }
		\item \small{ \textbf{DevOps/Systems:} Docker, Terraform (managed multi-cloud infra with \textbf{50+ resources}), Argo CD, Kubernetes (orchestrated \textbf{100+} pods), Prometheus, Grafana, GitHub Actions, FastAPI }
		\item \small{ \textbf{Languages:} Python (10+ automation projects), Golang (GitOps controllers, plugins) }
	\end{itemize}
	
	
	
	%-----------CERTIFICATIONS-----------
	\section{Certifications \& Achievements}
	\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt ]
		\item Delivered \textbf{3+ production-grade products} solo for clients in Kuwait and UK  (tech stack: MVC .NET, Azure).
		\item Ranked in the \textbf{Top 3 teams} out of 200+ participants at \textbf{TechMinds Hackathon} at IITM.
		\item Won \textbf{HackByte Hackathon} at IIITDM Jabalpur - Best API Design track among 50+ teams.
		\item Certified \textbf{Postman Student Expert} - designed and tested 20+ robust APIs.
	\end{itemize}
	
	
	%-------------------------------------------
\end{document}
